%#########%
% Preamble %
%#########%

% Set document class and load in packages

\documentclass[paper=a4]{scrartcl}

\usepackage[aux]{rerunfilecheck}
\usepackage{fontspec}
\usepackage[ngerman, english]{babel}
\usepackage[autostyle]{csquotes}
\usepackage[unicode]{hyperref}
\usepackage{bookmark}
\usepackage[dvipsnames, svgnames, table]{xcolor}
\usepackage{transparent}
\usepackage{CJKutf8}
\usepackage{tipa}
\usepackage{soul}
\usepackage{mdframed}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{tcolorbox}
\usepackage{multirow}

%#####%
% Body %
%#####%

% Set main font and initiate document

\setmainfont{Helvetica Neue}

\begin{document}

		%======================%
		% Title and opening passage %
		%======================%

		\begin{centering}

			\textbf{\huge Introduction to \LaTeX} \bigskip
		
			A Beginner's Guide \bigskip

		\end{centering}
	
		\begin{flushleft} 
	
			This is a simple guide that shall serve as an introduction to \LaTeX{} (\textipa{"lA:tEk} or \textipa{"leItEk}). Test paper. \bigskip

			\textit{*Please note that …} 

		\end{flushleft} 
			
		%=============%
		% What is LaTeX? %
		%=============%

		\begin{flushleft} 

			\textbf{1. What is \LaTeX?} \bigskip

			Add text here. 

		\end{flushleft} 

		%=============%
		% LaTeX Structure %
		%=============%

		\begin{flushleft} 

			\textbf{2. Structure of a \LaTeX{}-Document} \bigskip

			A \LaTeX{}-document consists of two main parts: 
			1.) the preamble and 2.) the body. 
			The preamble is where the fundamentals of the document are set up, including the type of document, format and packages (see XXX). 
			It may also contain metadata such as the the author, date or title. 
			The preamble is initiated by the command \textit{\textbackslash documentclass\{\}} and ends with the beginning of the main body. 
			The main body is where the actual text of the document is created through a combination of normal text and markup. 
			It always begins with the \textit{\textbackslash begin\{document\}} command and ends with the \textit{\textbackslash end\{document\}} command.
			Every \LaTeX{} document requires all three of the above command lines irregardless of the contents. 
			Thus, the general structure of a \LaTeX{} document is: 

		\end{flushleft} 

			\begin{minipage}{0.5\textwidth}
				\begin{mdframed}[userdefinedwidth=7.5cm, backgroundcolor=black!7] 
			
					\textcolor{blue}{\textbackslash documentclass}\textcolor{DarkGreen}{[}options\textcolor{DarkGreen}{]}\textcolor{DarkGreen}
						{\{}class\textcolor{DarkGreen}{\}} 
			
					\noindent \hspace{5mm} ... \bigskip{}
			
					\noindent \textcolor{blue}{\textbackslash begin}\textcolor{DarkGreen}{\{}document\textcolor{DarkGreen}{\}} 
			
					\noindent \hspace{5mm} ... \bigskip{}
			
					\noindent \textcolor{blue}{\textbackslash end}\textcolor{DarkGreen}{\{}document\textcolor{DarkGreen}{\}} 
			
				\end{mdframed}			
			\end{minipage}
			\begin{minipage}{0.1\textwidth}
						
					\[
						\begin{drcases*}
							\textcolor{white}{...} \\
							\textcolor{white}{...} \\
							\end{drcases*}
							preamble 
					\]								
					\[
						\begin{drcases*}
							\textcolor{white}{...} \\
							\textcolor{white}{...} \\
							\textcolor{white}{...} 					
							\end{drcases*}
							body 
					\]	
												
			\end{minipage}								

		\bigskip{}

		\begingroup
			\fontsize{9pt}{11pt}\selectfont

				Ex.) \bigskip{}

				\textcolor{blue}{\textbackslash documentclass}\textcolor{DarkGreen}{\{}minimal\textcolor{DarkGreen}{\}} 
				
				\textcolor{blue}{\textbackslash begin}\textcolor{DarkGreen}{\{}document\textcolor{DarkGreen}{\}} 
				
				Hello world!
				
				\textcolor{blue}{\textbackslash end}\textcolor{DarkGreen}{\{}document\textcolor{DarkGreen}{\}} 
		\endgroup		
			
		%=========== %
		% LaTeX-Syntax %
		%=========== %

		\begin{flushleft} 

			\textbf{3. \LaTeX-Syntax} \bigskip
			
			In \LaTeX{} special commands are used for typesetting a text or document. 
			These commands are usually a combination of special characters and letters, do not allow for any spaces and are case sensitive
				\footnote{
					\tiny Case sensitive means that upper- and lowercase are treated as distinct. For example, \textit{command1} and \textit{Command1}  	
					\tiny would be two different commands and not interchangeable. Case sensitivity is also a common source of error, as commands    
					\tiny must be entered as intended (e.g. \textbackslash\textit{LaTeX\{\}}  vs. \textit{\st{\textbackslash latex\{\}}}).
					}			
			. Similarly to the valency of a verb in language, \LaTeX{} commands can be classified by the number of arguments they take. 
			In general, they can be categorised into two major groups: \bigskip{}
			
			1.) Zero-Argument-Commands 
			
			2.) Non-Zero-Argument-Commands \bigskip{}
									
			%------------------------- %
			% Basic Commands %
			%------------------------- %			
			
			\textbf{3.1 Zero-Argument-Commands} \bigskip{}
			
			\foreignlanguage{english}{\enquote{Zero-Argument-Commands}} are commands that do not require any additional arguments - at least 
			on the surface level - and that can be used intransitively (i.e. on their own). 
			These commands generally consist of three components: 
			1.) a backslash, 2.) a simple word or phrase indicating the function of the command and 3.) (empty) curly brackets. 
			They can be notated as:
		
		\end{flushleft}

			\colorbox{yellow}{\textit{\textbackslash somecommand\{\}}} \bigskip

		\begingroup
			\fontsize{9pt}{11pt}\selectfont

				Ex.) \bigskip

				\textit{\textbackslash LaTeX\{\}} \hspace{10mm} – \hspace{5mm} displays the \foreignlanguage{english}{\enquote{LaTeX}} symbol (\LaTeX)

				\textit{\textbackslash noindent\{\}} \hspace{6.6mm} – \hspace{5mm} suppresses paragraph indentation

				\textit{\textbackslash bigskip\{\}} \hspace{9mm} – \hspace{5mm} creates a vertical empty space

		\endgroup		

		\begin{flushleft}

			Since basic commands like this do not take on any specified arguments, the curly brackets (for more detail see 3.2) may be left out. 
			While this normally does not entail any loss of function, it can lead to minor behavioural differences (such as inserting or deleting a space), 
			especially when the command is a direct part of the text: 

		\end{flushleft}
			
		\begingroup
			\fontsize{9pt}{11pt}\selectfont
			
				\textit{\textbackslash LaTeX is cool}  \hspace{10mm} vs. \hspace{10mm} \textit{\textbackslash LaTeX\{\} is cool}

			\begingroup
				\fontsize{7.5pt}{10pt}\selectfont			
		
					\hspace{1mm} (= \LaTeX is cool) \hspace{30mm} (= \LaTeX{} is cool)
			
			\endgroup

		\endgroup		

			%---------------------------------------%
			% Commands with Arguments %
			%---------------------------------------%			

		\begin{flushleft} 
		
			\textbf{3.2 Commands and Arguments}\bigskip

			\foreignlanguage{english}{\enquote{Non-Zero-Argument-Commands}} are commands that typically require an argument, 
			i.e. an object they can be applied to. 
			For example, the \textit{\textbackslash textit\{x\}} command that is used for italicising needs an object x (usually a word or text) it can
			refer to or else it would not execute. 
			This type of commands follows a similar syntax to the one seen in 3.1, with the exception that 
			a.) curly brackets cannot be empty and actively require an argument and 
			b.) facultative arguments (arguments that modify a command but are not required for the command to work) may be 
			passed on via square brackets. 
			Sometimes a command may also require more than one obligatory argument, which can be marked with additional curly brackets: 

		\end{flushleft}

			\colorbox{yellow}{\textit{\textbackslash somecommand[optional]\{obligatory\}\texttransparent{0.2}{\{obligatory\}}}} \bigskip

		\begingroup
			\fontsize{9pt}{11pt}\selectfont

				Ex. 2) \bigskip
				
				\textit{\textbackslash textit\{Hello world!\}} \hspace{27mm} – \hspace{5mm} puts specified text into italics
				
				\textit{\textbackslash documentclass[paper=a4]\{scrartcl\}} \hspace{4mm} – \hspace{5mm} sets class of document (and specifies paper size) 
				
				\textit{\textbackslash textcolor\{red\}\{Hello world!\}} \hspace{15mm} – \hspace{5mm} applies specified colour to object
								
		\endgroup

			%----------------------------------------------%
			% Line Breaks, Spaces and Indents %
			%----------------------------------------------%			

		\begin{flushleft} 
		
			\textbf{3.3 Line Breaks, Spaces and Indents} \bigskip			

			\LaTeX{} mainly disregards any in-code spaces or line breaks, i.e. they have no visual impact on the actual text document. 
			For example, a sentence can be spread across several lines of code without disrupting the text output.
			In the same way, any number of spaces can be inserted between code elements without them being transferred to the text document. 
			The only time where spacing matters is for commands, as they cannot be broken up. Compare:

		\end{flushleft}
					
			\begin{minipage}{0.45\textwidth}
				\begin{tcolorbox}[title=Code, colframe=blue!20, sharp corners, colback=white]
				
					I'm just 
				
					a 
				
					simple example trying \hspace{5mm} to make \hspace{8mm} my way
				 
					through \hspace{4mm} the universe.
				
				\end{tcolorbox} 
			
			\end{minipage}		
			\begin{minipage}{0.45\textwidth}
				\begin{tcolorbox}[title=Output, colframe=blue!20, sharp corners, colback=white]
				
					I'm just 
					a
					simple example trying     to make        my way
					through    the universe. \bigskip{}
				
					\vspace{5mm}
				
				\end{tcolorbox} 		
			\end{minipage}			

		\begin{flushleft} 
		
			To specifically include line breaks in a text, one may choose from various options such as:
			
			\begin{itemize}
				\setlength\itemsep{0em}
					\item <empty line> \hspace{5.5mm} (creates new line)
					\item \textit{\textbackslash newline} \hspace{13.75mm} (same as <empty line>)
					\item \textit{\textbackslash hfill \textbackslash break} \hspace{9mm} (same as <empty line>)
					\item \textit{\textbackslash bigskip} \hspace{14.75mm} (creates vertical space, ordinarily one line)
			\end{itemize}

		\end{flushleft}				

			\begin{minipage}{0.45\textwidth}
				\begin{tcolorbox}[title=Code, colframe=blue!20, sharp corners, colback=white]
				
					You don't need to see \bigskip{}
				
					my identification. \textcolor{blue}{\textbackslash newline}
				
					I'm the example you're 
				
					looking for. \textcolor{blue}{\textbackslash hfill \textbackslash break} 
				
					I can go about 
				
					my business. \textcolor{blue}{\textbackslash bigskip}\textcolor{DarkGreen}{\{\}} \bigskip
					
					Move along! 		
				
				\end{tcolorbox} 
			\end{minipage}		
			\begin{minipage}{0.45\textwidth}
				\begin{tcolorbox}[title=Output, colframe=blue!20, sharp corners, colback=white]
				
					You don't need to see
				
					my identification. \newline
					I'm the example you're 
					looking for. \hfill \break  
					I can go about 
					my business. \bigskip{}
				
					Move along! 		
				
					\vspace{8.4mm}				
										
				\end{tcolorbox} 	
					
			\end{minipage}			
			
		\begin{flushleft} 
		
			For horizontal spacing some of the more widely spread commands include:
			
			\begin{itemize}
				\setlength\itemsep{0em}
					\item <empty space> \hspace{6mm} (inserts a standard horizontal space)
					\item \textit{\textbackslash enspace} \hspace{17mm} (inserts a horizontal space of 0.5em)
					\item \textit{\textbackslash quad} \hspace{22.75mm} (inserts a horizontal space of 1em; can be stacked)
					\item \textit{\textbackslash qquad} \hspace{20.25mm} (inserts a horizontal space of 2em; same as 
						\textit{\textbackslash quad \textbackslash quad})					
					\item \textit{\textbackslash hskip<len>} \hspace{12.75mm} (inserts a space of specified length; can be negative)
					\item \textit{\textbackslash hspace\{<len>\}} \hspace{7mm} (inserts a space of specified length + 1 standard space; 
					
						\hspace{3.45cm} can be negative)	
					\item \textit{\textbackslash hfill} \hspace{25.5mm} (inserts rubber space that stretches acc. to available space)									\end{itemize}

		\end{flushleft}				

			\begin{minipage}{0.45\textwidth}
				\begin{tcolorbox}[title=Code, colframe=blue!20, sharp corners, colback=white]
								
					Hello there! \bigskip{}
				
					Hello \textcolor{blue}{\textbackslash enspace} there! \bigskip{}
				
					Hello \textcolor{blue}{\textbackslash quad} there! \bigskip{}
				
					Hello \textcolor{blue}{\textbackslash qquad} there! \bigskip{}
				
					Hello \textcolor{blue}{\textbackslash hskip}1.2cm there! \bigskip{}
				
					Hello \textcolor{blue}{\textbackslash hspace}\textcolor{DarkGreen}{\{}1.2cm\textcolor{DarkGreen}{\}} there! \bigskip{}
				
					\textcolor{blue}{\textbackslash hspace}\textcolor{DarkGreen}{\{}0.9cm\textcolor{DarkGreen}{\}} Hello
						\textcolor{blue}{\textbackslash hspace}\textcolor{DarkGreen}{\{}-2.1cm\textcolor{DarkGreen}{\}} there! \bigskip{}
				
					You \textcolor{blue}{\textbackslash hfill} are \textcolor{blue}{\textbackslash hfill} a \textcolor{blue}{\textbackslash hfill} bold
						\textcolor{blue}{\textbackslash hfill} one.
				
				\end{tcolorbox} 
			\end{minipage}		
			\begin{minipage}{0.45\textwidth}
				\begin{tcolorbox}[title=Output, colframe=blue!20, sharp corners, colback=white]
				
					Hello there!
				
					Hello \enspace there!

					Hello \quad there!

					Hello \qquad there!

					Hello \hskip1.2cm there!

					Hello \hspace{1.2cm} there!		
				
					\hspace{0.9cm} Hello \hspace{-2.1cm} there!							
				
					You \hfill are \hfill a \hfill bold \hfill one.
				
					\vspace{3.825cm}				
										
				\end{tcolorbox} 	
			\end{minipage}							

		\begin{flushleft} 
			
			Outside of environments (see XXX) the first line of a paragraph is always indented by default. 
			To manually insert indents one may use horizontal spacing commands such as the above, while
			the \textit{\textbackslash noindent} command removes the default indentation:

		\end{flushleft} 

			\begin{minipage}{0.45\textwidth}
				\begin{tcolorbox}[title=Code, colframe=blue!20, sharp corners, colback=white]
				
					Strong I am with indenting, but not that strong. 
					Twilight is upon me and soon night must fall. 
					\textcolor{blue}{\textbackslash bigskip} \bigskip
				
					\textcolor{blue}{\textbackslash noindent} Soon I will rest. Yes, forever \bigskip
				
					\textcolor{blue}{\textbackslash hspace}\textcolor{DarkGreen}{\{}0.3cm\textcolor{DarkGreen}{\}} 	sleep. Earned it, I have.			
								
				\end{tcolorbox} 
			\end{minipage}		
			\begin{minipage}{0.45\textwidth}
				\begin{tcolorbox}[title=Output, colframe=blue!20, sharp corners, colback=white]
				
					\hspace{0.3cm} Strong I am with indenting, but not that strong. 
					Twilight is upon me and soon night must fall. \bigskip
										
					Soon I will rest. Yes, forever 
					
					\hspace{0.3cm} sleep. 
					Earned it, I have.

					\vspace{1.725cm}				
													
				\end{tcolorbox} 
			\end{minipage}		

		\begin{flushleft} 
			
			Finally, in-code indents may serve as a simple way to structure and organise the code to make it more readable and accessible.
			
		\end{flushleft} 
		
			%----------------------------------------------------------------%
			% Comments, Special Characters and Quotation  %
			%----------------------------------------------------------------%			

		\begin{flushleft} 
		
			\textbf{3.4 Comments, Special Characters and Quotation} \bigskip			

			Comments in programming are explanations or annotations in the source code that intend to make the code easier for human readers to
			understand and that are usually ignored by the compiler or interpreter (and hence not executed). 
			In \LaTeX{} comments are marked through the percentage sign (\textit{\%}). 

		\end{flushleft} 
		
			% Example Comments

			\begin{minipage}{0.45\textwidth}
				\begin{tcolorbox}[title=Code, colframe=blue!20, sharp corners, colback=white]
				
					\textcolor{red}{\% Sets text to italics} \bigskip			

					\textcolor{blue}{\textbackslash textit}\textcolor{DarkGreen}{\{}Comment or comment not. There is no try.\textcolor{DarkGreen}{\}}
												
				\end{tcolorbox} 
			\end{minipage}		
			\begin{minipage}{0.45\textwidth}
				\begin{tcolorbox}[title=Output, colframe=blue!20, sharp corners, colback=white]
				
					\textit{Comment or comment not.} 

					\textit{There is no try.}
										
					\vspace{0.8cm}				
													
				\end{tcolorbox} 
			\end{minipage}		
	
		\begin{flushleft} 
		
			Special characters like \textit{\textbackslash}, \textit{\$} or \textit{\%} are often used as operators in \LaTeX{} and thus need
			a little bit of work around to be included in-text. 
			Some characters can be used by simply prefixing a backslash, others require a unique command: \bigskip

			% Table special characters
			
			\begin{tabular}{
				| p{3cm} | p{3cm} | p{3cm} | p{3cm} |
				}
				\hline
				\rowcolor{red!30}
					\multicolumn{4}{| c |}{\textbf{Special Characters}} \\
				\hline
					\rowcolor{red!10}				
						\multicolumn{2}{| c |}{\textbf{Backslash Commands}} & \multicolumn{2}{c |}{\textbf{Unique Commands}} \\
				\hline
					\rowcolor{red!10}
						\multicolumn{1}{| c |}{\textbf{Command}} & 
						\multicolumn{1}{ c |}{\textbf{Character}} & 
						\multicolumn{1}{ c |}{\textbf{Command}} & 
						\multicolumn{1}{ c |}{\textbf{Character}} \\
				%\textbf{Command} & \textbf{Character} & \textbf{Command} & \textbf{Character} \\
				\hline
					\textbackslash \# & \# & \textbackslash textbackslash & \textbackslash \\
					\textbackslash \$ & \$ & \textbackslash textasciicircum & \textasciicircum \\
					\textbackslash \% & \% & \textbackslash textasciitilde & \textasciitilde \\
					\textbackslash \& & \& & \textbackslash infty & \infty \\
					\textbackslash \{ & \{ & \textbackslash triangle & \triangle \\
					\textbackslash \} & \} & \textcolor{lightgray}{...} & \textcolor{lightgray}{...} \\
					\textbackslash \_ & \_ & & \\
					\textcolor{lightgray}{...} & \textcolor{lightgray}{...} & & \\
				\hline				
			\end{tabular}
			
			\bigskip
			
			% Quotation 
			
			Quotation marks are prone to displaying errors, depending on the editor that is used. 
			
			One of the safest ways to include quotation marks in a text is via the \textit{\textbackslash enquote\{\}} function from the 
			\foreignlanguage{english}{\enquote*{csquotes}} package, 
			which can be conjoined with the \textit{\textbackslash foreignlanguage\{\}} function from the \foreignlanguage{english}{\enquote*{babel}} package to 
			allow for language appropriate quotation.
			Both packages need to be loaded in via the \textit{\textbackslash usepackage\{\}} command (see XXX) in the preamble and can be
			modified with optional arguments such as the desired languages for the \foreignlanguage{english}{\enquote*{babel}} package and 
			different styles for the \foreignlanguage{english}{\enquote*{csquotes}} package (for example, \foreignlanguage{english}{\enquote*{autostyle}} 
			continuously adapts the quote style to the current document language).
			
			\bigskip

			The standard command \textit{\textbackslash enquote\{\}} inserts double quotation marks, but can be modified with an asterisk to
			switch to single quotation marks (i.e. \textit{\textbackslash enquote*\{\}}). 
			Finally, quotes may be nested with \textit{\textbackslash enquote\{\textbackslash enquote\{\}\}} to achieve quotation within quotation.	

			\bigskip

		\end{flushleft}
					
			% Example for quotation marks 

				\begin{tcolorbox}[title=Code, colframe=blue!20, sharp corners, colback=white]
				
					\textcolor{red!40}{\% Load packages in preamble} 
					
						\bigskip
					
					\textcolor{blue!40}{\textbackslash usepackage}\textcolor{DarkGreen!40}{[}\textcolor{black!40}{english, french, german}\textcolor{
						DarkGreen!40}{]}\textcolor{DarkGreen!40}{\{}\textcolor{black!40}{babel}\textcolor{DarkGreen!40}{\}} 

					\textcolor{blue!40}{\textbackslash usepackage}\textcolor{DarkGreen!40}{[}\textcolor{black!40}{autostyle}\textcolor{
						DarkGreen!40}{]}\textcolor{DarkGreen!40}{\{}\textcolor{black!40}{csquotes}\textcolor{DarkGreen!40}{\}} 
					
						\bigskip
				
					\textcolor{blue}{\textbackslash foreignlanguage}\textcolor{DarkGreen}{\{}english\textcolor{DarkGreen}{\}\{}\textcolor{
						blue}{\textbackslash enquote}\textcolor{DarkGreen}{\{}Do or do not. There is no try.\textcolor{DarkGreen}{\}\}} 
						\textcolor{blue}{\textbackslash bigskip} \bigskip
						
					\textcolor{blue}{\textbackslash foreignlanguage}\textcolor{DarkGreen}{\{}english\textcolor{DarkGreen}{\}\{}\textcolor{
						blue}{\textbackslash enquote}*\textcolor{DarkGreen}{\{}Do or do not. There is no try.\textcolor{DarkGreen}{\}\}} 
						\textcolor{blue}{\textbackslash bigskip} \bigskip

					\textcolor{blue}{\textbackslash foreignlanguage}\textcolor{DarkGreen}{\{}german\textcolor{DarkGreen}{\}\{}\textcolor{
						blue}{\textbackslash enquote}\textcolor{DarkGreen}{\{}Do or do not. There is no try.\textcolor{DarkGreen}{\}\}}  \bigskip
											
					\textcolor{blue}{\textbackslash enquote}\textcolor{DarkGreen}{\{}Yoda, \textcolor{blue}{\textbackslash enquote}\textcolor{
						DarkGreen}{\{}Darth Vader\textcolor{DarkGreen}{\}} and Luke\textcolor{DarkGreen}{\}} 
						
				\end{tcolorbox} 

				\begin{tcolorbox}[title=Output, colframe=blue!20, sharp corners, colback=white]
				
					\foreignlanguage{english}{\enquote{Do or do not. There is no try.}} \bigskip
					
					\foreignlanguage{english}{\enquote*{Do or do not. There is no try.}} \bigskip

					\foreignlanguage{german}{\enquote{Tu es oder tu es nicht. Es gibt kein Versuchen.}} \bigskip
					
					\enquote{Yoda, \enquote{Darth Vader} and Luke}

				\end{tcolorbox} 
			
			\bigskip

			%---------------------%
			% Environments  %
			%---------------------%			

		\begin{flushleft}
			
			\textbf{3.5 Environments} \bigskip			

			In \LaTeX{} environments are macros that can be used to apply specific formats to a section of the document, 
			for example to align or centre text, to generate a table or to create lists. 
			To initiate an environment the \textit{\textbackslash begin\{\}} command is used, 
			which must be closed with the \textit{\textbackslash end\{\}} command. 
			Options must be placed after the environment name to avoid any collisions.
			Finally, environments can in themselves contain (further) environments, which, however, 
			must be closed before the overarching environment ends: 

		\end{flushleft}
		
			% Environment notation

			\begin{minipage}{0.5\textwidth}		
				\begin{mdframed}[userdefinedwidth=7cm, backgroundcolor=black!7] 
			
					\textcolor{blue}{\textbackslash begin}\textcolor{DarkGreen}{\{}environment1\textcolor{DarkGreen}{\}}\textcolor{DarkGreen}
						{[}options\textcolor{DarkGreen}{]} 

					\hspace{5mm} \textcolor{blue!30}{\textbackslash begin}\textcolor{DarkGreen!30}{\{}\textcolor{
						black!30}{environment2}\textcolor{DarkGreen!30}{\}}\textcolor{
						DarkGreen!30}{[}\textcolor{black!30}{options}\textcolor{DarkGreen!30}{]} 
			
					\hspace{10mm} ... 

					\hspace{5mm} \textcolor{blue!30}{\textbackslash end}\textcolor{DarkGreen!30}{\{}\textcolor{black!30}{environment2}\textcolor{
						DarkGreen!30}{\}}
						
					\textcolor{blue}{\textbackslash end}\textcolor{DarkGreen}{\{}environment1\textcolor{DarkGreen}{\}}

				\end{mdframed}				
			\end{minipage}	
			
			\bigskip	
					
			% Example for environments 

			\begin{minipage}{0.45\textwidth}
				\begin{tcolorbox}[title=Code, colframe=blue!20, sharp corners, colback=white]
				
					\textcolor{blue}{\textbackslash begin}\textcolor{DarkGreen}{\{}center\textcolor{DarkGreen}{\}} \bigskip
					
						\hspace{0.3cm} You've failed, your highness.
						
						\hspace{0.3cm} I'm an example, 
						
						\hspace{0.3cm} like my father before me. \bigskip
					
					\textcolor{blue}{\textbackslash end}\textcolor{DarkGreen}{\{}center\textcolor{DarkGreen}{\}}
													
				\end{tcolorbox} 
			\end{minipage}		
			\begin{minipage}{0.45\textwidth}
				\begin{tcolorbox}[title=Output, colframe=blue!20, sharp corners, colback=white]
				
					\begin{center}
					
						You've failed, your highness.
						I'm an example, 
						like my father before me.
					
					\end{center}
					
				\vspace{1.4cm}				
													
				\end{tcolorbox} 
			\end{minipage}		

		\begin{flushleft} 
			
			Some of the most important environments are:
			
			% Create list for different environments 
			
			\begin{itemize}
			
				\item Text Alignment
				
					\begin{itemize}					
						\item \textbf{\textit{flushleft}} (left aligns the text)
						\item \textbf{\textit{center}} (centres the text)
						\item \textbf{\textit{flushright}} (right aligns the text)
					\end{itemize}					
					
				\item Enumerations/Lists
										
					\begin{itemize}					
						\item \textbf{\textit{itemize}} (creates a list with bullet points)
						\item \textbf{\textit{enumerate}} (creates a list with numbers)
						\item \textbf{\textit{description}} (creates an unmarked list of a bold and normal element)
					\end{itemize}					

				\item Graphics
										
					\begin{itemize}					
						\item \textbf{\textit{figure}} (allows for embedding of graphical elements such as images)
						\item \textbf{\textit{tabular}} (creates a table)
					\end{itemize}					

				\item Others
										
					\begin{itemize}					
						\item \textbf{\textit{document}} (creates the main body of the document)
						\item \textbf{\textit{verbatim}} (displays the source text without being interpreted)
					\end{itemize}					

			\end{itemize}	
												
		\end{flushleft} 

			%------------------%
			% 3.6 Nesting  %
			%------------------%			

		\begin{flushleft}
			
			\textbf{3.6 Nesting} \bigskip			

			Sometimes it is desirable to apply several commands to an object at once 
			(for example, when combining bold font with italics).
			In \LaTeX{} this can simply be achieved by \foreignlanguage{english}{\enquote*{nesting}} 
			(or \foreignlanguage{english}{\enquote*{stacking}}) commands:
			
			\bigskip
			
			\colorbox{yellow}{\textit{\textbackslash command1\{\textbackslash command2\{…\}\}}} \bigskip

		\end{flushleft}
		
		%======== %
		% Packages %
		%======== %

		\begin{flushleft} 

			\textbf{4. Packages} \bigskip
			
			Packages are macros that supplement the base functionality of \LaTeX{} by adding on
			new functions or features. 
			To use packages they first need to be loaded in, which can be done by including them in the 
			preamble via the \textit{\textbackslash usepackage\{\}} directive. 
			Once a package is loaded in, any function from that package may be called upon 
			(e.g. the \textit{\textbackslash enquote\{\}} function from the \foreignlanguage{english}{\enquote*{csquotes}} package).
			While the order in which packages are listed in the preamble is generally free, it may matter depending on
			package dependencies (especially for language-related packages).
			Below is a list of some common packages:

			\bigskip			

			% Table packages

			\begin{tabular}{
				| p{3cm} | p{5cm} | p{5cm} | 
				}
				\hline
				\rowcolor{green!20}
					\multicolumn{3}{| c |}{\textbf{Useful packages}} \\
				\hline
					\rowcolor{green!7.5}
						\multicolumn{1}{| c |}{\textbf{Package}} & 
						\multicolumn{1}{ c |}{\textbf{Function}} & 
						\multicolumn{1}{ c |}{\textbf{Additional Information}} \\
				\hline
					rerunfilecheck & 
					provides additional rerun warnings if auxiliary files have changed &
					files to be checked can be passed on as optional arguments;
					\textit{[aux]} turns on checking for all auxiliary files \\
				\hline
					fontspec & 
					for extensive font settings and customisation &
					\\
				\hline				
					babel & 
					enables multilanguage support for document and ensures typographical accuracy for a variety of languages 
					(e.g. quotation marks, dates) &
					languages to be used in the document can be passed on as optional arguments via \textit{[ ]}; 
					the last language listed is the main language of the document \\
				\hline				
					hyperref & 
					useful for creating PDFs and cross-references (e.g. hyperlinks, bookmarks, page numbers) &
					\textit{[unicode]} may be passed on to keep the pdf string in unicode encoding \\
				\hline				
					amsmath & 
					provides extensive options for displaying and customising mathematical equations &
					\\
				\hline				
					tikz & 
					for creating simpler and more complex graphical elements (e.g. lines, dots, geometric shapes, paths) in \LaTeX{} &
					\\
				\hline				
					microtype & 
					enhances general appearance of document (e.g. protrusion, interword spacing, kerning) &
					\\
				\hline				
			\end{tabular}
			
			\bigskip
			
			Not only are there countless packages to choose from in \LaTeX{}, 
			but individual packages can get quite extensive on their own, 
			as they usually offer a great array of different options and settings.
			It is nearly impossible to keep track of all the different .
			Luckily, most \LaTeX{} packages are well-documented and offer a source. 

		\end{flushleft} 			

			\colorbox{yellow}{texdoc <package>} \bigskip

		%===== %
		% Font %
		%===== %

		%\begin{flushleft} 

		%	\textbf{5. Dummy title} \bigskip			

		%	Dummy text					

		%\end{flushleft} 		
		
		
		
%					\begin{center}
					
%						You've failed, your highness.
%						I'm an example, 
%						like my father before me.
					
%					\end{center}
		
%	\end{flushleft}								

\end{document}
